\begin{frame}
  \tableofcontents[currentsection,hideothersubsections]
\end{frame}

\begin{frame}{How to learn this course}
\begin{block}{How to learn this course?}
\begin{itemize}
    \item Follow the lecture
    \item Finish the homework on time
\end{itemize}
\end{block}

\begin{block}{How to learn this course well?}
\begin{itemize}
    \item Don't do something stupid (including \textbf{violation of honor code}, late submission)
    \item Don't be afraid of asking and \textbf{exploring}
    \item Do as many labs as you can
\end{itemize}
\end{block}
\end{frame}

\begin{frame}
\begin{block}{Tips}
\begin{itemize}
\item This course mainly focuses on the correctness of your code; you are not expected to improve the efficiency of code.
\item Every \textbf{error} (mostly in red) means something is wrong. Fix it even when the outputs are sometimes right.
\item Please be aware that a program which is right sometimes and wrong the other time, is \textbf{wrong}.
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{About honor code}
First, please remember that you are \textbf{strongly encouraged} to discuss! Being brave to discuss with DALAO is an essential step to become a DALAO.

\begin{block}{What you should not do?}
\begin{itemize}
    \item Don't show any code! 
    \item Don't copy others' code! 
\end{itemize}
\end{block}
Most of time, when you are violating honor code, you yourself know that you are doing something bad. 

Please be aware that everytime you trying to violate the honor code but thinking that you can escape from the concequence, you are essentially challenging your instructor and TA group. All the code will be examed by specific tools, and almost all the tricks you can come up with are pale and useless. 
\end{frame}